\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-04-29 HOPS/photometry/ms.tex
updated intro

\section{Introduction}
\par
A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Given such far-reaching significance, a primary goal of current Galactic star-formation research has been to develop such a comprehensive narrative of star formation.  This importance is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.
\par
However, many details and key ingredients  are not well understood \citep{mo07}, and are needed to complete our picture of the star formation process.  In particular, one critical aspect, the connection between the raw building blocks and the conditions for star formation provided by the underlying environment and its impact on the final product (the star) is not well characterized \citep{dunham}.
\par
Protostars provide useful laboratories for studying the link between the local environmental conditions and the star itself.  At the protostellar stage, the incipient star is still strongly connected with the local environment, and it is in the protostellar phase that the stellar mass is accumulated and protoplanetary disks are created \citep{c2d09}.  A detailed characterization of the protostellar evolution, thus, allows us to directly follow the evolution of raw materials.
\par
Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.
\par
We use a combination of strategies for {\it HOPS}\  to mitigate both challenges (i) and (ii), above.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  
\par
Second, we focus on the nearby star-forming region Orion.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.

(2) Include sufficient number of protostars in a diverse set of environmental conditions, and (3)

Further, we focus on the nearby Orion star-forming region.

To properly remove the degeneracies from (i), we require sufficient spatial resolution and multi-wavelength measurements to disentangle the emission and morphology of the various components that make up the protostar and its immediate environ.  We also require sufficiently large number of protostars in a diverse set of environmental conditions to properly investigate the role of initial conditions on the fundamental properties of the emergent star.  Further, the effects of extinction (ii, above) and the required sensitivity to detect and study a large sample of protostars is mitigated by using focusing on infrared and longer wavelengths.  The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical \citep{extinction}.
\par
Besides alleviating interstellar extinction, \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is the defining characteristic of a protostar. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.
\par
The combination of the nearby Orion star-forming region and the near- to far-infrared capabilities of \herschel\ and \spitzer\ allow us to meet our main requirements (above).   
\par
This paper summarizes the results from the photometry component of the \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath).  This paper is one in a series describing the results from HOPS (\eg\ Stutz \etal\ 2013, Kryukova \etal\ 2014, Fischer \etal\ 2016, Furlan \etal\ 2016).  Our emphasis in this paper will be on the photometry catalog and the observed properties of protostars.  Section~\ref{sec:sample} describes our observational sample and technique.  Section~\ref{sec:dp} describes our data processing and assembly of final maps.  Section~\ref{sec:phot} discusses photometry of individual sources.  Sections~\ref{sec-results}~\&~\ref{sec:discussion} present and discuss our findings.  And, finally, our conclusions are summarized in Section~\ref{sec:conc}.

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for the HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  Our original sample of 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 410 sources in the final sample included here.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 410 objects in this contribution.

>>>>

\section{Introduction}
A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Given such far-reaching significance, a primary goal of current Galactic star-formation research has been to develop such a comprehensive narrative of star formation.  This importance is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.
However, many details and key ingredients  are not well understood \citep{mo07}, and are needed to complete our picture of the star formation process.  In particular, one critical aspect, the connection between the raw building blocks and the conditions for star formation provided by the underlying environment and its impact on the final product (the star) is not well characterized \citep{dunham}.
Protostars provide useful laboratories for studying the link between the local environmental conditions and the star itself.  At the protostellar stage, the incipient star is still strongly connected with the local environment, and it is in the protostellar phase that the stellar mass is accumulated and protoplanetary disks are created \citep{c2d09}.  A detailed characterization of the protostellar evolution, thus, allows us to directly follow the evolution of raw materials.
Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.  Finally, (iii)  \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is a defining characteristic of protostars. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.
The  \herschel\ Orion Protostar Survey (HOPS) Open Time Key Program (PI: S. T. Megeath) was motivated by the availability of sensitive far-infrared measurements to address the challenges, (i) -- (iii), mentioned above.  HOPS uses a combination of strategies to mitigate these issues.  First, we use multi-wavelength measurements to disentangle the protostar's components.  Multi-wavelength measurements are useful because they directly connect the emergent spectral properties with the underlying physical structure and conditions of said protostar component.  As these conditions vary between the components, they also vary in the emergent emission.  
Second, we focus on the nearby star-forming region Orion \citep{orion}.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.
Finally, the inclusion of \herschel\ data, in particular, allowed us to directly measure the emission from the protostellar envelopes, and mitigate the effects of extinction.   The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical wavelengths \citep{extinction}.  The unprecedented sensitivity afforded by \herschel\ at far-infrared wavelengths allowed us to efficiently sample a large number of protostars.
This paper is one in a series describing the results from HOPS (\eg\ Stutz \etal\ 2013, Kryukova \etal\ 2014, Fischer \etal\ 2016, Furlan \etal\ 2016).  Our emphasis in this paper will be on the photometry catalog and the observed properties of protostars.  Section~\ref{sec:sample} describes our observational sample and technique.  Section~\ref{sec:dp} describes our data processing and assembly of final maps.  Section~\ref{sec:phot} discusses photometry of individual sources.  Sections~\ref{sec-results}~\&~\ref{sec:discussion} present and discuss our findings.  And, finally, our conclusions are summarized in Section~\ref{sec:conc}.

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for the HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  Our original sample of 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 410 sources in the final sample included here.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, and sdcs\cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 410 objects in this contribution.
